Differential Expression - MSSM-Penn-Pitt - DLPFC - Dx

### 2020-05-18 individual-cohorts/MSSM-Penn-Pitt_DLPFC_DE.Rmd
typo

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx", "ageOfDeath", "RIN2", "RIN", "IntronicRate", "IntragenicRate")war
random_effect <- c("Institution", "Reported_Gender")
```

>>>>

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx", "ageOfDeath", "RIN2", "RIN", "IntronicRate", "IntragenicRate")
random_effect <- c("Institution", "Reported_Gender")
```
